### 2022-03-24 preprint.tex
Deploying to gh-pages from @ emuise/assessingRepresentation@e6f7d8b3346749e9bac99a18aaf2a543eb608cd0 🚀

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

@@

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0003-3404-3220}{Evan, R.\,Muise}%
%
\,\textsuperscript{1}\quad %
Nicholas, C.\,Coops%
%
\,\textsuperscript{1}\quad %
Txomin\,Hermosilla%
%
\,\textsuperscript{2}\quad %
Stephen, S.\,Ban%
%
\,\textsuperscript{3}

\textsuperscript{1}\,Department of Forest Resources Management,
University of British Columbia\quad \textsuperscript{2}\,Canadian Forest
Service (Pacific Forestry Centre)\quad \textsuperscript{3}\,BC Parks,
Ministry of Environment and Climate Change Strategy

\textbf{Correspondance to:}\\
Evan, R. Muise --- \texttt{evanmuis@student.ubc.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill
Protected areas (PA) are an effective means of conserving biodiversity
and protecting suites of valuable ecosystem services. Currently, many
nations and international governments use proportional area protected as
a critical metric for assessing progress towards biodiversity
conservation. However, this and other common metrics do not assess the
effectiveness of PA networks, nor do they assess how representative PA
are of the ecosystems they aim to protect. Topography, stand structure,
and land cover are all key drivers of biodiversity within forest
environments, and are well suited as indicators to assess the
representation of PA. Here we examine the protected area network in
British Columbia, Canada, through these drivers derived from freely
available data and remote sensing products across the provincial
biogeoclimatic ecosystem classification system. We examine biases in the
protected area network by elevation, forest disturbances, and forest
structural attributes, including height, cover, and biomass by comparing
a random sample of protected and unprotected pixels. Results indicate
that PA are commonly biased towards high elevation and alpine land
covers, and that forest structural attributes of the park network are
often significantly different in protected vs unprotected areas (426 out
of 496 forest structural attributes found to be different; p \textless{}
0.01). Analysis of forest structural attributes suggests that
establishing additional PA could ensure representation of various forest
structure regimes across British Columbia's ecosystems. We conclude that
these approaches using free and open remote sensing data are highly
transferable, and can be accomplished using consistent datasets to
assess PA representations globally.

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

>>>>

%!TEX TS-program = xelatex
\documentclass[10pt,oneside]{article}
\usepackage[fontsize=9pt]{scrextend}

@@

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}

\geometry{includemp,
            letterpaper,
            top=2.4cm,
            bottom=2.4cm,
            left=1.0cm,
            right=1.0cm,
            marginparwidth=5cm,
            marginparsep=1.0cm}

\usepackage[singlelinecheck=off]{caption}

\captionsetup{
  font={small},
  labelfont={bf},
  format=plain,
  labelsep=quad
}

\usepackage{floatrow}

\floatsetup[figure]{margins=hangright,
              facing=no,
              capposition=beside,
              capbesideposition={center,outside},
              floatwidth=\textwidth}

% \floatsetup[table]{margins=hangright,
%              facing=no,
%              capposition=beside,
%              capbesideposition={center,outside},
%              floatwidth=\textwidth}

@@

\setcounter{secnumdepth}{5}

\usepackage{titlesec}

\titleformat{\section}[block]
{\normalfont\large\sffamily}
{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}

\titleformat{\subsection}[runin]
{\normalfont\fontseries{b}\selectfont\filright\sffamily}
{\thesubsection.}{.5em}{}

\titleformat{\subsubsection}[runin]
{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}

\fancypagestyle{firstpage}
{
   \fancyhf{}
   \renewcommand{\headrulewidth}{0pt}
   \fancyfoot[R]{\footnotesize\ccby}
   \fancyfoot[L]{\footnotesize\sffamily\today}
}

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}

\usepackage{tikz}
\begin{document}
\tikz [remember picture, overlay] %
\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
\pagestyle{normal}
\thispagestyle{firstpage}

\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}

\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
manuscripts using markdown and github actions}}}

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0003-3404-3220}{Evan, R.\,Muise}%
%
\,\textsuperscript{1}, %
Nicholas, C.\,Coops%
%
\,\textsuperscript{1}, %
Txomin\,Hermosilla%
%
\,\textsuperscript{2}, %
Stephen, S.\,Ban%
%
\,\textsuperscript{3}
\vskip 1em
\textsuperscript{1}\,Department of Forest Resources Management,
University of British Columbia; \textsuperscript{2}\,Canadian Forest
Service (Pacific Forestry Centre); \textsuperscript{3}\,BC Parks,
Ministry of Environment and Climate Change Strategy\\
\vskip 1em
\textbf{Correspondance to:}\\
Evan, R. Muise --- \texttt{evanmuis@student.ubc.ca}\\
}
\end{flushleft}

\vskip 2em
\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
\vskip 2em
\noindent

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
Protected Areas\\Remote Sensing\\Forest Structure\\Forest
Disturbances\\Land Cover\\Ecological Classifications\\}
}

Protected areas (PA) are an effective means of conserving biodiversity
and protecting suites of valuable ecosystem services. Currently, many
nations and international governments use proportional area protected as
a critical metric for assessing progress towards biodiversity
conservation. However, this and other common metrics do not assess the
effectiveness of PA networks, nor do they assess how representative PA
are of the ecosystems they aim to protect. Topography, stand structure,
and land cover are all key drivers of biodiversity within forest
environments, and are well suited as indicators to assess the
representation of PA. Here we examine the protected area network in
British Columbia, Canada, through these drivers derived from freely
available data and remote sensing products across the provincial
biogeoclimatic ecosystem classification system. We examine biases in the
protected area network by elevation, forest disturbances, and forest
structural attributes, including height, cover, and biomass by comparing
a random sample of protected and unprotected pixels. Results indicate
that PA are commonly biased towards high elevation and alpine land
covers, and that forest structural attributes of the park network are
often significantly different in protected vs unprotected areas (426 out
of 496 forest structural attributes found to be different; p \textless{}
0.01). Analysis of forest structural attributes suggests that
establishing additional PA could ensure representation of various forest
structure regimes across British Columbia's ecosystems. We conclude that
these approaches using free and open remote sensing data are highly
transferable, and can be accomplished using consistent datasets to
assess PA representations globally.

\vskip 2em
\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
\vskip 2em
